\thispagestyle{empty}
\section*{Abstract}
Text abstraktu v svetovom jazyku je potrebný pre integráciu do medzinárodných informačných systémov (napr. The Network Digital Library of Theses and Dissertations).

{ \it Príklad  abstraktu (upravený):} \\
NOVÁK, Vladimír: Index Policies for Dynamic and Stochastic Problems [Bachelor
Thesis], Comenius University in Bratislava, Faculty of Mathematics, Physics and Informatics, Department of Applied Mathematics and Statistics; Supervisor: Mgr. Peter Jacko, PhD., Bratislava, 2011, 38p.

In our work we investigate the Whittle's index policy derivation framework in
the Markov decision process environment. We analyze a model for the multi-class job
scheduling for user with abandonment, with the objective of minimizing the total
holding costs and abandonment penalties. The work provides analytical solution of an
optimal index rule for the case in which there are 1 or 2 users in the system. For
the case with more users we use recent results from the multi-armed restless bandits
approach and derive a new simple index rule, denoted by AJN, for the idling and
the non-idling system. This index rule is proposed to use also in the system with
arrivals. We also report on an exhaustive study of numerical experiments for both
systems, in which we compare AJN index rule with  certain two standard  rules. This computational study suggests that our rule is almost always superior or equivalent to the other rules, and it is often optimal.

\begin{flushleft}
  \textbf{Keywords:} Markov Decision Process, Multi-armed Restless Bandit, Whittle Index, Index Policies,  Bellman Equation
\end{flushleft}